---
title: "Practical Machine Learning Course Project Writeup"
output: html_document
---

The goal of the project is to predict the manner in which people did the exercise. This is the **classe** variable in the dataset. The data can be found on http://groupware.les.inf.puc-rio.br/har

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=5, fig.height=2.5, comment="",
                      echo=TRUE, warning=FALSE, message=FALSE)
```
```{r load_R_file, cache=FALSE, echo=FALSE}
knitr::read_chunk('project.R')
```

# Loading the data

Firstly, we load necessary libraries and set a seed for random procedures.

```{r init, cache=TRUE}
```

Secondly, we load training and testing datasets.

```{r load-data, cache=TRUE}
```

Finally, we subset these columns (attributes) which are complete. That is, we 
remove those which have NAs or *#DIV/0!* string.

```{r preprocess, cache=TRUE}
```

# Building the model

Since the input dataset is large, we split it into training and validation
datasets in 60% and 40% proportions, respectively.

We will investigate kNN classifier. We perform reapeated cross-validation to
choose the best *n*. Since all attibutes are numeric, we scale and center 
features. We set accuracy as an evaluation metric in this step.

```{r build-model, cache=TRUE}
```

The final value used for the model is *k* = `r knnFit$finalModel$k`. Overall
accuracy is estimated to `r round(cmat$overall[1], 2)`.

# Predicting outcomes

Now we can predict from the test set.

```{r predict-outcomes, cache=TRUE}
```
```{r show-answers, chache=TRUE}
print(answers)
```

Finally, we save the outputs.

```{r save-outputs, cache=TRUE}
```
